Exploring Crete's Macroecology based on its soil Microbial Interactome

### 2023-12-30 manuscript.tex
restrure the flow of intro

@@

Global soil microbiome studies \citep{Delgado-Baquerizo2018} and \citep{Bahram2018} and the biogeography \citep{Martiny2006} \citep{Guerra2020}, \citep{Labouyrie2023} yet there are significant blind spots \citep{Guerra2020}. The most resolute study is \citep{Karimi2020}

Islands are nature's labs \citep{Whittaker2017} and in soil microbes \citep{Li2020} and fungi \citep{Delavaux2021}
Ultimately islands can set the ground to represent ecosystems with data and complex interactions \citep{Davies2016}.
\citep{Vogiatzakis2008_crete}
\citep{Vogiatzakis2016}

\citep{Sfenthourakis2017}
\citep{Vogiatzakis2008_med}
Genome Standards Consortium \citep{Field2011}, FAIR data \citep{Wilkinson2016}, unrestricted \citep{Amann2019},
rich metadata and platforms of hosting open data like European Soil Data Centre \citep{Panagos2022}

Here we present

>>>>

Soil ecosystems are the cornstone of terrestrial habitats, biodiversity and henceforth human activities.
Complex interactions of multiple systems, nutrient cycling, atmosphere, climate, biogeochemical cycles and biodiversity 
across all forms of life, fauna, flora, bacteria, archaea, fungi, viruses. 
Bacteria and archaea are considered major drivers for the functionality of soil.
They infuence and are infuenced by their environments and their community structure 
is defies their macroscopic functionality.
Global soil microbiome studies \citep{Delgado-Baquerizo2018} and \citep{Bahram2018} and the biogeography \citep{Martiny2006} \citep{Guerra2020}, \citep{Labouyrie2023} yet there are significant blind spots \citep{Guerra2020}. The most resolute study is \citep{Karimi2020} which exemplified the 
remarkable complexity of soil bacterial communuties and the requirement of  dense samplings and isolated systems.

Island Sampling Day project and the 
Genome Standards Consortium \citep{Field2011} "put standards into action" and the 
18th workshop. 
The choice of an island
Islands are nature's labs \citep{Whittaker2017} and in soil microbes \citep{Li2020} and fungi \citep{Delavaux2021}
Ultimately islands can set the ground to represent ecosystems with data and complex interactions \citep{Davies2016}.
A large scale study in the confined space of the island of Crete, a miniature continent.

@@

\citep{Vogiatzakis2008_crete}
\citep{Vogiatzakis2016}

\citep{Sfenthourakis2017}
\citep{Vogiatzakis2008_med}

Integration of prior knowledge and 
Genome Standards Consortium \citep{Field2011}, FAIR data \citep{Wilkinson2016}, unrestricted \citep{Amann2019},
rich metadata and platforms of hosting open data like European Soil Data Centre \citep{Panagos2022}

Interactomes as a driver of community composition. Microbial interactions challenges \citep{Faust2021} cohesion?

In this study, we investigate
